Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{27. Response:}

\begin{quote}
\color{blue}
We reworded the sentence according to the reviewer's suggestion:

``It has been found
in highly vagile species in the nymphalid genus \emph{Vanessa} that
dispersal has homogenized populations due to gene flow, as 
vagile species seem to be genetically homogeneous in their
populations Wahlberg N, Rubinoff D (2011).''
\end{quote}

\textbf{28. Reviewer's Comment:}
Page 9, Satyrinae subsection, sentence beginning “It appears that the 
radiation...”: replace “picked up” with “detected”.

\textbf{28. Response:}

\begin{quote}
\color{blue}
We replaced the words according to the reviewer's suggestion:
\end{quote}

\textbf{29. Reviewer's Comment:}
Page 9, Conclusions section, sentence beginning “Moreover, some of these
splits...”: replace “splits” with “shifts”.

\textbf{29. Response:}
\begin{quote}
\color{blue}
We replaced the word according to the reviewer's suggestion:
\end{quote}

### 2015-01-14 MS_revised.tex
comment 30

\section*{Conclusions}
We found that even though MEDUSA estimated several diversification
shifts in the maximum clade credibility tree of Nymphalidae, only a few
of these shifts were found in more than 90\% of the trees from the
posterior distribution. In the literature, it is common practice that
conclusions are based on the shifts estimated on the maximum clade
credibility tree. However, by using a MultiMEDUSA approach, we found
that for this Nymphalidae dataset some of these shifts might be greatly
affected by phylogenetic uncertainty. Moreover, some of these shifts can
be recovered either as increases or decreases in net diversification
rate depending on the tree from the posterior distribution that was used
for analysis. This means that contradictory conclusions would be made if
only the maximum clade credibility tree was used for analysis. We
recommend that all datasets should be analyzed using both approaches,
MEDUSA and MultiMEDUSA, in order to test whether the results are robust
when phylogenetic uncertainty is taken into account.

>>>>

\section*{Conclusions}
We found that even though MEDUSA estimated several diversification
shifts in the maximum clade credibility tree of Nymphalidae, only a few
of these shifts were found in more than 90\% of the trees from the
posterior distribution. In the literature, it is common practice that
conclusions are based on the shifts estimated on the maximum clade
credibility tree. However, by using a MultiMEDUSA approach, we found
that for this Nymphalidae dataset some of these shifts might be greatly
affected by phylogenetic uncertainty. Moreover, some of these shifts can
be recovered either as increases or decreases in net diversification
rate depending on the tree from the posterior distribution that was used
for analysis. This means that contradictory conclusions would be made if
only the maximum clade credibility tree was used for analysis.
We recommend that all datasets should be analyzed using the MultiMEDUSA
approach in order to test whether the results are robust
when phylogenetic uncertainty is taken into account.
